Project proposal: Explanations for unexplained effect size heterogeneity

### 2023-06-18 supplement/supplement_A.qmd
osf links to figures/tables
rendered supplements

```{r Figure A1, echo=FALSE, out.width = '100%'}
knitr::include_graphics("../figures/supplement/supplement_A_fig1.png")
```

_Figure A1._ Bias in heterogeneity estimates in the absence of unreliability in primary studies (i.e., reliability = 1). The x-axis indicates average effect size and the y-axis estimated heterogeneity in standard deviations. Columns indicate the nominal true heterogeneity standard deviation $\tau$. Due to truncation in Pearson's $r$ or translation to Fisher's $z$ these values may differ from actual true heterogeneity standard deviation (black solid lines).

@@

```{r Figure A2, echo=FALSE, out.width = '100%'}
knitr::include_graphics("../figures/supplement/supplement_A_fig2.png")
```

_Figure A2._ Removal of the dependency between effect size and sampling variance removes the positive bias in heterogeneity estimates for larger true heterogeneity when using Pearson's $r$. The x-axis indicates average effect size and the y-axis estimated heterogeneity in standard deviations averaged across 1e3 repetitions. Columns indicate the nominal true heterogeneity standard deviation $\tau$. Due to truncation in Pearson's $r$ or translation to Fisher's $z$ these values may differ from actual true heterogeneity standard deviation (black solid lines).

>>>>

```{r Figure A1, echo=FALSE, out.width = '90%'}
knitr::include_graphics("../figures/supplement/supplement_A_fig1.png")
```

_Figure A1. Bias in heterogeneity estimates in the absence of unreliability in primary studies (i.e., reliability = 1). The x-axis indicates average effect size and the y-axis estimated heterogeneity in standard deviations. Columns indicate the nominal true heterogeneity standard deviation $\tau$. Due to truncation in Pearson's $r$ or translation to Fisher's $z$ these values may differ from actual true heterogeneity standard deviation (black solid lines). Code to reproduce figure: osf.io/8ygwj._

@@

```{r Figure A2, echo=FALSE, out.width = '90%'}
knitr::include_graphics("../figures/supplement/supplement_A_fig2.png")
```

_Figure A2. Removal of the dependency between effect size and sampling variance removes the positive bias in heterogeneity estimates for larger true heterogeneity when using Pearson's $r$. The x-axis indicates average effect size and the y-axis estimated heterogeneity in standard deviations averaged across 1e3 repetitions. Columns indicate the nominal true heterogeneity standard deviation $\tau$. Due to truncation in Pearson's $r$ or translation to Fisher's $z$ these values may differ from actual true heterogeneity standard deviation (black solid lines). Code to reproduce figure: osf.io/8ygwj._

### 2023-06-18 supplement/supplement_C.qmd
osf links to figures/tables
rendered supplements

```{r Figure C1, echo=FALSE, out.width = '100%'}
knitr::include_graphics("../figures/supplement/supplement_C_fig1.png")
```

_Figure C1._ Inflation of effect sizes decreases with lower reliability SD leading to larger net negative bias in heterogeneity, especially for large effect sizes and moderate heterogeneity. The x-axis indicates average effect size and the y-axis estimated heterogeneity in standard deviations. Columns indicate nominal true between-studies standard deviation and rows indicate reliability standard deviation. Due to truncation in Pearson's $r$ these values may differ from actual true heterogeneity standard deviation (black solid lines). Each dashed line correspond to an average reliability in primary studies.

@@

```{r Figure C2, echo=FALSE, out.width = '100%'}
knitr::include_graphics("../figures/supplement/supplement_C_fig2.png")
```

_Figure C2._ Expected inflation of effect sizes decreases with larger number of meta-analyzed when heterogeneity is absent or small and average effect size is small. The x-axis indicates average effect size and the y-axis estimated heterogeneity in standard deviations. Columns indicate nominal true between-studies standard deviation and rows indicate number of meta-analyzed studies. Due to truncation in Pearson's $r$ these values may differ from actual true heterogeneity standard deviation (black solid lines). Each dashed line correspond to an average reliability in primary studies.

>>>>

```{r Figure C1, echo=FALSE, out.width = '90%'}
knitr::include_graphics("../figures/supplement/supplement_C_fig1.png")
```

_Figure C1. Inflation of effect sizes decreases with lower reliability SD leading to larger net negative bias in heterogeneity, especially for large effect sizes and moderate heterogeneity. The x-axis indicates average effect size and the y-axis estimated heterogeneity in standard deviations. Columns indicate nominal true between-studies standard deviation and rows indicate reliability standard deviation. Due to truncation in Pearson's $r$ these values may differ from actual true heterogeneity standard deviation (black solid lines). Each dashed line correspond to an average reliability in primary studies. Code to reproduce figure: osf.io/8ygwj._

@@

```{r Figure C2, echo=FALSE, out.width = '90%'}
knitr::include_graphics("../figures/supplement/supplement_C_fig2.png")
```

_Figure C2. Expected inflation of effect sizes decreases with larger number of meta-analyzed when heterogeneity is absent or small and average effect size is small. The x-axis indicates average effect size and the y-axis estimated heterogeneity in standard deviations. Columns indicate nominal true between-studies standard deviation and rows indicate number of meta-analyzed studies. Due to truncation in Pearson's $r$ these values may differ from actual true heterogeneity standard deviation (black solid lines). Each dashed line correspond to an average reliability in primary studies. Code to reproduce figure: osf.io/8ygwj._
